The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-21 paper/main.tex
add discussion of companion fraction uptick

@@

>>>>

Further, Fig.~\ref{fig:frac_model_3} shows that going from apparent 
radii of $2r_\oplus$ to $\approx 1.4r_\oplus$, the fraction of detected 
planets with binary companions increases by $\approx 6-12\%$, depending on the 
assumed value of $Z_2/Z_0$.
Let the fraction of detected planets from primaries at a given apparent radius 
be $F_1(r\a)$.
In the planet-less secondaries case, one can then see by analyzing 
Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically that 
$F_1(2r_\oplus)/F_1(2r_\oplus/\sqrt{2}) \approx 1.19$.
%check_companion_fractions.py, and LB's notes 2017/12/21.0
More intuitively, this ``shift'' is a feature of any radius distribution that 
declines at large radii, and flattens below some cutoff $r_c$.
Thinking only about dilution from primaries is simplest:
at apparent radii $r\a < r_c/\sqrt{2}$, relatively more planets will be 
``diluted'' into the given $r\a$, since there are more planets in 
the undiluted distribution from $r\a$ to $\sqrt{2}r\a$.
This prediction is compared against current measurements in 
Sec.~\ref{sec:discussion}.

@@

\paragraph{Fraction of detected planets with binary companions vs. apparent 
radius}
A prediction of Fig.~\ref{fig:frac_model_3} is that the fraction of detected 
planets with binary companions increases by $\approx 6-12\%$ going from 
$2r_\oplus$ to $\approx 1.4r_\oplus$.
In \citet{ziegler_robo-ao_2017}'s recent summary of the Robo-AO KOI survey, 
they reported the nearby star fraction rates for planet candidates binned by 
Earths ($r\a < 1.6r_\oplus$), Neptunes ($1.6r_\oplus < r\a < 3.9 r_\oplus$), 
Saturns ($3.9r_\oplus < r\a < 9 r_\oplus$), and Jupiters ($r\a > 9r_\oplus$).
The nearby star rates and their $1\sigma$ uncertainties 
(following~\cite{burgasser_binarity_2003}'s procedure) are as
follows:
\begin{itemize}
    \item Earths: $16.3 \pm 1.0\%$, from 1480 systems.
    \item Neptunes: $13.0 \pm 0.8\%$, from 2058 systems.
    \item Saturns: $13.6 \pm 2.0\%$, from 338 systems.
    \item Jupiters: $19.0 \pm 2.8\%$, from 247 systems.
\end{itemize} 
where the absolute normalization of the rates are less than those typical for 
Sun-like stars at least in part because of Robo-AO's sensitivity 
(see~\citealt{ziegler_robo-ao_2017}'s Fig.~2).
The uptick in the companion rate for Jupiters is likely tied to a large 
astrophysical false positive rate~\citep{santerne_sophie_2012}.
Although the data do not support as large of an uptick in companion rate 
as our Fig.~\ref{fig:frac_model_3} suggests, going from Neptunes to Earths,
there is still a weak increase in the detected planet companion fraction.
